draft 1

### 2016-07-06 finalwriteup/draft.rmd
ran individual folds

@@

Another strategy to mitigate risk is to agree to track employee hours, and stop work once the fixed consulting fee has been depleted. Then, negotiate further fees, or variations, with the client. This approach may satisfactorily reduce a consultant’s financial risk, however, may cause friction between the client and the consultant and affect potential repeat custom. Especially if the project followed a predictable process but the hours inflated beyond expectation (a common situation), consultants may prefer to wear losses or endure marginable profits to preserve their client relationship. Consultants may believe it is in their best interest to maintain a reliable, trustworthy reputation in their industry above creating financial friction. Clearly, there is not a straightforward contractual solution to reducing the financial risk taken on by consultant's who offer fixed fees in complex projects. In many industries, the reality of fixed flat fee structures are unavoidable businesses conform to survive.

@@

@Lovallo2003 tackled the psychology behind the high failure rates of executives in predicting costs of projects such as manufacturing plant construction, mergers and acquisitions, large infrastructure and software development. Their theory stems from Kahneman's work on decision-making that won him the nobel prize for economics in 2002. His research argues that a person's natural optimistic view of their own skills leads to consistent underestimation of the time and risks involved in a project. A manager optimistically sees challenges in a project as something that can be overcome by the team's high skill level, and downplays or ignores the risk of problems that are out of the team's control. It is for this reason that it does not matter if the project is broken down to the highest level of detail for cost prediction, all complex projects are at risk of encountering a multitude of problems that the manager could never foresee. Each problem has a low chance of occurring, but in combination the risk is much greater [@Lovallo2003].

>>>>

* Abstracts allow readers to quickly decide whether the research is relevant to their own interests
* get at your main argument quickly

*explain the purpose, goal methods, leave out results?

* why did you do the study?, what is the problem
* is it a general problem or something specific
* why is it important?
* why should someone read your essay?
* what is your main claim?

* discuss variables and your approaches
* describe evidence to support your claim
* overview of most important sources

* Results: answer , was hypothesis supported

* implications of your work, meaning

@@

Another strategy to mitigate risk is to agree to track employee hours, and stop work once the fixed consulting fee has been depleted. Then, negotiate further fees, or variations, with the client. This approach may satisfactorily reduce a consultant’s financial risk, however, may cause friction between the client and the consultant and affect potential repeat custom. Especially if the project followed a predictable process but the hours inflated beyond expectation (a common situation), consultants may prefer to wear losses or endure marginable profits to preserve their client relationship. Consultants may believe it is in their best interest to maintain a reliable, trustworthy reputation in their industry above creating financial friction. Clearly, there is not a straightforward contractual solution to reducing the financial risk taken on by consultant's who offer fixed fees in complex projects. In many industries, the reality of fixed flat fee structures are unavoidable and businesses conform to survive.

@@

@Lovallo2003 tackled the psychology behind the high failure rates of executives in predicting costs of projects such as manufacturing plant construction, mergers and acquisitions, large infrastructure and software development. Their theory stems from Kahneman's work on decision-making that won him the Nobel Prize for economics in 2002. His research argues that a person's natural optimistic view of their own skills leads to consistent underestimation of the time and risks involved in a project. A manager optimistically sees challenges in a project as something that can be overcome by the team's high skill level, and downplays or ignores the risk of problems that are out of the team's control. It is for this reason that it does not matter if the project is broken down to the highest level of detail for cost prediction, all complex projects are at risk of encountering a multitude of problems that the manager could never foresee. Each problem has a low chance of occurring, but in combination the risk is much greater [@Lovallo2003].
